---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/ipasnhistory.svg?branch=master)](https://travis-ci.org/hrbrmstr/ipasnhistory) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/ipasnhistory/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/ipasnhistory)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ipasnhistory)](https://cran.r-project.org/package=ipasnhistory)

# ipasnhistory

Retrieve Announcement History for IP Addresses

## Description

IP ASN History is an open source project (<https://github.com/D4-project/IPASN-History>)
to figure out the ASN announcing an IP and the closest prefix announcing it
at a specific date. Methods are provided to query CIRCL-LU's API endpoint
and/or a local API endpoint.

## What's Inside The Tin

The following functions are implemented:

- `ip_asn_db_meta`:	Returns meta informations about the information currently stored in the database at the specified endpoint
- `ip_history`:	Retrieve IP ASN advertisement history
- `mass_cache`:	Populate the API cache
- `mass_query`:	Mass query IP ASN history info
- `timedelta`:	Construct a time delta value for 'ip_history()'

## Installation

```{r install-ex, eval=FALSE}
install.packages("ipasnhistory", repos="https://cinc.rud.is/")
# or 
remotes::install_git("https://sr.ht.com/~hrbrmstr/ipasnhistory.git")
# or
remotes::install_gitlab("hrbrmstr/ipasnhistory")
# or (if you must)
remotes::install_github("hrbrmstr/ipasnhistory")
```

## Usage

```{r lib-ex}
library(ipasnhistory)

# current version
packageVersion("ipasnhistory")

```

```{r}
str( ip_asn_db_meta(), 2 )

str( ip_history("146.185.222.49"), 3 )

str( ip_history("146.185.222.49", first="2018-11-01", last="2018-11-25"), 3 )
```

## ipasnhistory Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
